Paper 2: Vitamin D

### 2017-09-22 doc/vitaminD.Rmd
added functions to figure out values for graphs

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "MET",
           "VitaminD",
           "PTH",
           "UDBP",
           "udbpCrRatio",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "OralContraceptive",
           "dmStatus"),
  strata = c("fVN"),
  data = ds,
  factorVars = c("Sex", "Ethnicity", "OralContraceptive", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "udbpCrRatio"),
        quote = FALSE,
        noSpaces = TRUE)
```

@@

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot("vitdStatus", "log(udbpCrRatio)", 
            "Vitamin D Status",
            "log uVDBP:Creatinine")

@@

@@

dsBase %>% 
  interac_plot(yvar = "PTH",
               intvar = "Season",
               ylab = "Parathyroid Hormone (pmol/L)") #Serum 25(OH)D (nmol/L) #Parathyroid Hormone (pmol/L)
```

@@

ds %>% 
  interac_plot(yvar = "VitaminD",
               intvar = "Season",
               ylab = "Serum 25(OH)D (nmol/L)")
```

>>>>

subchar_vitd_base <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "MET",
           "VitaminD",
           "PTH",
           "UDBP",
           "udbpCrRatio",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "OralContraceptive",
           "dmStatus"),
  strata = c("fVN"),
  data = ds,
  factorVars = c("Sex", "Ethnicity", "OralContraceptive", "dmStatus")
) %>% 
  print(nonnormal = c("UDBP",
                      "udbpCrRatio"),
        quote = FALSE,
        noSpaces = TRUE) %>% 
  knitr::kable()

ds %>%
  dplyr::select(VN, PTH) %>%
  dplyr::group_by(VN) %>%
  na.omit() %>%
  summarise(n = n())
```

@@

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot("vitdStatus", "log(udbpCrRatio)", 
            "Vitamin D Status",
            "log uVDBP:Creatinine (μg/mmol)")

# value
vitd %>%
  dplyr::group_by(vitdStatus) %>% 
  dplyr::summarise(Median = median(log(udbpCrRatio)), 
                   IQR = IQR(log(udbpCrRatio))
                   )

@@

tab_nums(gee_vitd_baseline, "GEE results for uVDBP at baseline (predictor) with 25(OH)D and (outcomes), adjusted for follow-up duration (in months), baseline age, sex, ethnicity, physical activity (MET), BMI, diabetes status, and seasonality; subjects with deficient vitamin D status at baseline excluded (n = 713).")

@@

dsBase %>% 
  interac_plot(yvar = "PTH",
               intvar = "Season",
               ylab = "Parathyroid Hormone (pmol/L)") #Serum 25(OH)D (nmol/L) #Parathyroid Hormone (pmol/L)

rms::ols(VitaminD ~ udbpCrRatio * Season, data = dsBase)
```

@@

ds %>% 
  interac_plot(yvar = "VitaminD",
               intvar = "Season",
               ylab = "Serum 25(OH)D (nmol/L)")

rms::ols(VitaminD ~ udbpCrRatio * Season, data = ds)
```
